% Per-paper personal contribution statements (required for compendium theses).
\chapter*{Statement of Personal Contribution}
\label{coauthor-statements}
\addcontentsline{toc}{chapter}{Statement of Personal Contribution}

\paragraph{Chapter 2 -- Adaptive Survey Sampling via Ad Platforms.}
Coauthored with Dante Donati (Columbia University).
The project grew out of an earlier,
separate study with Dante Donati, which prompted my idea to drive many
advertisements through a single optimization engine via the advertising
platform's API. I developed the methodology---formulating adaptive stratified
recruitment as the minimization of the variance of a post-stratification--weighted
estimator under budget constraints, together with the Bayesian scheme for
estimating unknown per-stratum recruitment costs---and I implemented all of the
production software and open-source tooling, including the optimization engine,
the Messenger survey chatbot, the API integrations, and the monitoring dashboard.
Dante secured the funding, including for the U.S. gold-standard survey; we
designed the survey instrument jointly. The idea to evaluate the methodology by
its mean absolute deviation from gold-standard benchmark surveys was mine, while
Dante and his research assistants fielded the U.S. survey, produced the cost
analysis, and carried out the comparative deviation analysis. The comparison
against Prolific and LLM-generated digital twins was conceived, collected, and
analyzed entirely by Dante. I compiled and analyzed the multi-country deployment
evidence using other studies I worked on separately. Dante and I drafted the manuscript in
roughly equal measure.

\paragraph{Chapter 3 -- Facebook Ads vs. Malaria.}
Coauthored with Dante Donati (Columbia University), Victor Orozco-Olvera (DIME,
World Bank), and Ana Maria Mu\~noz-Boudet (EMBED, World Bank).
This study was conceived and funded within the World Bank, where Victor
Orozco-Olvera and Ana Maria Mu\~noz-Boudet are staff. The four authors jointly developed the cluster-randomized
study design, to which I contributed the geographic targeting strategy. Dante led
the survey design, while I built the experimental platform developed in
Chapter~\ref{ch:survey-sampling}, designed the dwelling-type stratification, and
ran recruitment. I devised and designed the individual-level feed experiment,
wrote the initial draft of the paper, and conducted the initial regression
analysis, which Dante subsequently reproduced and refined. The incorporation and
analysis of the administrative health-facility data, together with the associated
cost-effectiveness analysis, were led by Dante, who also carried out the
additional regressions and analysis requested in review and did the vast majority of the
final writing, polishing, and journal submission, with supporting help from all the other authors. 

\paragraph{Chapter 4 -- Impact Evaluation of UNICEF's Bebbo Parenting App.}
Coauthored with Yasemin Kisbu (UNICEF ECARO).
Yasemin Kisbu led coordination with UNICEF ECARO, provided access to the Bebbo
application and its usage analytics, framed the early-childhood-development theory
of change, and designed the survey instrument and its parenting and knowledge
measures. I proposed several candidate evaluation designs, from which Yasemin
selected the final randomized-encouragement design; I then carried out all
participant recruitment and survey data collection through the platform developed
in Chapter~\ref{ch:survey-sampling}, extracted and analyzed the app-usage data,
and conducted all of the statistical analysis. I wrote the initial draft of the
paper, and Yasemin contributed to revising the manuscript.

\cleardoublepage
